Unifying intra- and inter-specific variation in tropical tree mortality

### 2018-07-23 ms/manuscript.Rnw
fixed typo

Additionally, the partitioning of mortality rates into both carbon-dependent and carbon-independent effects allowed us to not only estimate their relative contribution, but also how species traits affect each. Like many other studies \cite{King:1994vg, Ruger:2011cv, Kunstler:2016km}, our analyses highlighted the importance of light competition in influencing tropical tree demographic rates. Specifically, we found that that the removal of the growth-dependent hazard term resulted in a substantial reduction in the model's ability to correctly distinguish survivors from those that died (Table~\ref{table1}). This suggests deficiencies in carbon budgets are a major contributor to tree death on Barro Colorado Island.

Our analyses support previous research that advocated that wood density, species maximum size and light demand important explanatory variables of inter-specific variation in tropical rainforests \cite{Poorter:2006tq, Chave:2009iy}. Specificially, we show that light demanding species are not only more susceptible to both low growth rates and growth-independent hazards, but also exhibited shallower declines in growth-dependent hazards with increasing growth rates. By contrast, both high dbh or wood density species were found to be more tolerant of growth-independent hazards, corrobrating evidence reported elsewhere\cite{Chave:2009iy, Kraft:2010kq}. However, our analyses also revealed that high wood density species were also more tolerant of low growth rates, and thus, better able to tolerate shade and competiton \cite{vanGelder:2006exa, Kunstler:2016km}.

@@

A species' maximum dbh was determined from the data, by taking the 95th percentile.

@@

\subsection*{Evaluating model skill}
Predictive skill was quantified by estimating the average log loss across 10-folds for held-out data, $\bar{\mathcal{L}}$ (Fig. \ref{fig1}). Logarithmic loss -- commonly known as log loss, $\mathcal{L}$, measures the skill of a model by penalizing incorrect predictions, based on how wrong the predicted probability is from the observed outcome, $S_i$ (Fig. \ref{fig1}C). Lower $\mathcal{L}$ implies greater skill. The average log loss across all individuals for the $k$th fold of held-out data, $\mathcal{L}_k$, is then
\begin{equation} \label{eq:logloss}
\mathcal{L}_k = - \frac1{N_k}\,\sum_{i=1}^{N_k}\left(S_i\,\log(p_{i,t_2\rightarrow t_3}) + ( 1 - S_i)\,\log(1 - p_{i,t_2\rightarrow t_3})\right),
\end{equation}
where $N_k$ refers to the number of observations in fold.

>>>>

Additionally, the partitioning of mortality rates into both carbon-dependent and carbon-independent effects allowed us to not only estimate their relative contribution, but also how species traits affect each. Like many other studies \cite{King:1994vg, Ruger:2011cv, Kunstler:2016km}, our analyses highlighted the importance of light competition in influencing tropical tree demographic rates. Specifically, we found that that the removal of the growth-dependent hazard term resulted in a substantial reduction in the model's ability to correctly distinguish survivors from those that died (Table~\ref{table:1}). This suggests deficiencies in carbon budgets are a major contributor to tree death on Barro Colorado Island.

Our analyses support previous research that advocated that wood density, species maximum size and light demand important explanatory variables of inter-specific variation in tropical rainforests \cite{Poorter:2006tq, Chave:2009iy}. Specificially, we show that light demanding species are not only more susceptible to both low growth rates and growth-independent hazards, but also exhibited shallower declines in growth-dependent hazards with increasing growth rates. By contrast, both high dbh or wood density species were found to be more tolerant of growth-independent hazards, corrobrating evidence reported elsewhere \cite{Chave:2009iy, Kraft:2010kq}. However, our analyses also revealed that high wood density species were also more tolerant of low growth rates, and thus, better able to tolerate shade and competiton \cite{vanGelder:2006exa, Kunstler:2016km}.

@@

A species' maximum dbh was determined from the data, by taking the 95th percentile observed for each species.

@@

\subsection*{Evaluating model skill}
Predictive skill was quantified by estimating the average log loss across 10-folds for held-out data, $\bar{\mathcal{L}}$ (Fig. \ref{fig1}). Logarithmic loss -- commonly known as log loss, $\mathcal{L}$, measures the skill of a model by penalizing incorrect predictions, based on how wrong the predicted probability is from the observed outcome, $S_i$ (Fig. \ref{fig1}C). Lower $\mathcal{L}$ implies greater skill. The average log loss across all individuals for the $k$th fold of held-out data, $\mathcal{L}_k$, is then
\begin{equation} \label{eq:logloss}
\mathcal{L}_k = - \frac1{N_k}\,\sum_{i=1}^{N_k}\left(S_i\,\log(p_{i,t_2\rightarrow t_3}) + ( 1 - S_i)\,\log(1 - p_{i,t_2\rightarrow t_3})\right),
\end{equation}
where $N_k$ refers to the number of observations in fold.
}
